\documentclass{article}

\usepackage[english]{babel} 
\usepackage{amsmath,amsfonts,amssymb}
\usepackage{graphicx}
\usepackage{braket}

\title{Notes on MGO}
\author{Arthur Adriaens}

\begin{document}
\maketitle

\section{GO}
GO assumes $\lambda$ is the shortest lenghtscale, suppose a stationary wavefield $\psi$ is governed by a linear wave equation
\begin{equation}
    \hat{\mathcal{D}}(\mathbf{x},-i\partial_\mathbf{x})\psi(\mathbf{x})
    \label{eq:BasicGO}
\end{equation}
With $D$ the dispersion kernel, and suppose further that $\psi$
can be partitioned into a rapidly varying phase $\theta$ and a
slowly varying envelope $\phi$:
\begin{equation}
    \psi(\mathbf{x}) = \phi(\mathbf{x})e^{i\theta(\mathbf{x})}
\end{equation}
Then it can be shown that $\theta$ and $\phi$ asymptotically
satisfy the following two relations:

\begin{enumerate}
    \item The local dispersion relation:
\begin{equation}
    \mathcal{D} [\mathbf{x},\partial_\mathbf{x} \theta(\mathbf{x})] = 0
\end{equation}
    \item The envelope transport equation
\begin{equation}
    2\mathbf{v}(\mathbf{x})^\intercal \partial_\mathbf{x}\phi(\mathbf{x}) + [\nabla\cdot\mathbf{v}(\mathbf{x})]\phi(\mathbf{x}) = 0
\end{equation}
\end{enumerate}

\noindent
Where $\mathcal{D}(\mathbf{x},\mathbf{k})$ is the Weyl symbol of
$\hat{\mathcal{D}}(\mathbf{x},-i\partial_x)$ (appendix \ref{appendix:Weyl}) and 
\begin{equation}
    \mathbf{v}(\mathbf{x}) \stackrel{.}{=} \partial_\mathbf{k}\mathcal{D}(\mathbf{x},\mathbf{k})|_{\mathbf{k}=\partial_\mathbf{x}\theta(\mathbf{x})}
\end{equation}
is proportional to the local group velocity.
If we neglect dissipation, thus assuming
$\hat{D}$ to be Hermitian and consequently, both 
$\mathcal{D}$ and $\mathbf{v}$ real. Then, the envelope transport equation can be cast as a conservation relation:
\begin{equation}
    \nabla\cdot[|\phi(\mathbf{x})|^2\mathbf{v}(\mathbf{x})] = 0
\end{equation}
I.e conservation of wave action flux.

The local dispersion relation defines a (2N-1) dimensional
volume in the 2N-D phase space with coordinates ($\mathbf{x},\mathbf{k}$). For coherent wavefields that have a single wavevector $\mathbf{k}(\mathbf{x})$ (or a finite superposition of such wavevectors), one can identify
\begin{equation}
    \mathbf{k}(\mathbf{x}) = \partial_\mathbf{x}\theta(\mathbf{x})
\end{equation}
Such that $\mathbf{k} $ is restricted to an N-D surface
contained within the (2N-1)-D volume (which N-D surface is
dictated by initial conditions). This N-D surface is called
the \textit{ray manifold} which is a Lagrangian manifold.
\section{Metaplectic Geometrical Optics}
Rather than describing waves as propagating in some
configuration space with coordinates $\mathbf{x}$ according to
pseudo-differential equation of the form (\ref{eq:BasicGO}), it
is more natural to describe waves as state vectors $\ket{\psi}$
in a Hilbert space being acted upon by operators. Then, partial
differential equations that govern wavefields can be understood
as projections of the invariant wave equations 
\begin{equation}
    \hat{D}(\hat{\mathbf{x}},\hat{\mathbf{k}})\ket{\psi} = \ket{0}
\end{equation}
on a particular basis.

\appendix
\section{Wigner-Weyl transform}
\label{appendix:Weyl}
The Wigner-Weyl transform (WWT, denoted as $\mathbb{W}$)
maps a given operator $\hat{A}(\hat{\mathbf{z}})$ to a corresponding phase-space function $\mathcal{A}(\mathbf{z})$ , called the 
\textit{Weyl symbol} of $\hat{A}$, as
\begin{eqnarray}
    \mathcal{A}(\mathbf{z}) &= \mathbb{W}[\hat{A}(\hat{\mathbf{z}})]\\
                            &\stackrel{.}{=} \int d\mathcal{\mathbf{\zeta} }\frac{i \mathbf{\zeta}^\intercal \mathtt{J_{2N}\mathbf{z}}}{(2\pi)^N} \text{tr}[e^{-i \mathbf{\zeta}^\intercal \mathtt{J}_{2N} \hat{\mathbf{z}}}\hat{A}]
\end{eqnarray}
With the integral taken over the phase space. and
\begin{equation}
    \mathtt{J}_{2N} = 
    \left(
    \begin{matrix}
        0_N & I_N\\
        -I_N & 0_N\\
    \end{matrix}
    \right)
\end{equation}
The inverse WWT maps a phase-space function to an operator:
\begin{eqnarray}
    \hat{A}(\mathbf{z}) &= \mathbb{W}^{-1}[\mathcal{A}(\mathbf{z})]\\
                        &\stackrel{.}{=} \int \frac{d\mathbf{z}'d\mathcal{\mathbf{\zeta} }}{(2\pi)^{2N}}\mathcal{A}(\mathbf{z}')e^{-i \mathbf{\zeta}^\intercal \mathtt{J}_{2N} \mathbf{z}' + i \mathbf{\zeta}^\intercal \mathtt{J}_{2N} \hat{\mathbf{z}}}
\end{eqnarray}

\end{document}
